Choosing and rating harmonies

### 2020-08-14 simulations_MMPD6.Rmd
README update

The output table has the value of MMPD (normalized median maximum pairwise distances), max_pd (un-normalized maximum pairwise distances), r(Rank of max_pd), gt_MMPD(global threshold of MMPD indicator) and gt_maxpd(global threshold of max_pd indicator).

@@

```{r diffnull_3levels}

@@

# histograms of MMPD when levels are different
When all distributions of response variables are generated from normal, how do the histogram looks

>>>>

The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator).

@@

# Levels and Power of the test statistic

<!-- ```{r diffnull_3levels} -->

<!-- ``` -->

@@

# Permutation test

To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis. If the null hypothesis is true, changing the exposure would have no effect on the outcome. By randomly shuffling the exposures we can make up as many data sets as we like. If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.

<!-- # ```{r} -->
<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
<!-- #  -->
<!-- # har1 <- harmonies[1,] -->
<!-- #  -->
<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
<!-- #  -->
<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
<!-- # data1 -->
<!-- #  -->
<!-- # data1 %>% unnest(sim_dist) %>% -->
<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
<!-- #  -->
<!-- # response = "sim_dist" -->
<!-- #  -->
<!-- # MMPD_distribution <- data1 %>% -->
<!-- #   select(-dist) %>%  -->
<!-- #   unnest(sim_dist) %>%  -->
<!-- #   list() %>%  -->
<!-- #   global_threshold(harmony_tbl = har1, -->
<!-- #                    response = "sim_dist", -->
<!-- #                    dist_distribution = "normal", -->
<!-- #                    dist_ordered = TRUE, -->
<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
<!-- #  -->
<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
<!-- #  -->
<!-- # ``` -->
<!-- #  -->
